Flesh Simulation in the Field of Animation

### 2020-04-05 LaTeX-Master-Vorlage/chapter/paper.tex
experiments

The images in Fig. \ref{fig:stretchtest} show four of the resulting objects of this example. They show step $0$ (initial cube), $8$, $16$ and $24$ for a tetrahedral and hexahedral mesh. The result is very good, no artefacts can be seen. There is no obvious difference recognizable whether we took a hexahedral or a tetrahedral mesh. The snapshots are taken with the help of the software OpenFlipper\footnote{https://www.graphics.rwth-aachen.de/software/openflipper/}.

@@

>>>>

The images in Fig. \ref{fig:stretchtest} show four of the resulting objects of this example. They show step $0$ (initial cube), $8$, $16$ and $24$ for a tetrahedral and hexahedral mesh. The result is very good, no artefacts can be seen. There is no obvious difference recognizable whether we took a hexahedral or a tetrahedral mesh. All snapshots in this chapter are taken with the help of the software OpenFlipper\footnote{https://www.graphics.rwth-aachen.de/software/openflipper/}.

@@

Fig. \ref{fig:res} shows the results with a higher resolution of $30$ compared to a lower resolution of $10$. All other input variables are the same. The figure shows the results of the deformation step $25$. We can see that a higher resolution clearly gives us much nicer results.

\begin{figure}[!ht]
\centering
\begin{subfigure}{.47\textwidth}
  \centering
  % include first image
  \includegraphics[width=.8\linewidth]{resources/default_zoom_tet.png}  
  \caption{Resolution of 10}
  \label{fig:res_1}
\end{subfigure}
\begin{subfigure}{.47\textwidth}
  \centering
  % include second image
  \includegraphics[width=.8\linewidth]{resources/res_zoom_tet.png}  
  \caption{Resolution of 30}
  \label{fig:res_2}
\end{subfigure}
\caption{Results with a different resolution on a tetrahedral mesh}
\label{fig:res}
\end{figure}
